Manuscript_Github_Pchabaudi_boilerplate

### 2022-08-04 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_qusage.Rmd
Add some comments

maxcol <- my_max(stagesTrans_ht.mat)
mincol <- my_max(stagesTrans_ht.mat*-1)*-1

ht <- Heatmap(t(stagesTrans_ht.mat),
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        cluster_column_slices = FALSE,
        na_col = 'white',
        row_split = factor(str_extract(colnames(stagesTrans_ht.mat),
                                   pattern = 'pirs|^L|^S|AAPL|ChAPL'),
                              levels = unique(str_extract(colnames(stagesTrans_ht.mat),
                                   pattern = 'pirs|^L|^S|AAPL|ChAPL'))),
        row_order = colnames(stagesTrans_ht.mat),
        row_gap = unit(.5,"cm"),
        row_names_gp = gpar(fontsize = 9),
        border = TRUE,
        col = colorRamp2(c(mincol,
                           0,
                           maxcol/4,
                           maxcol/2,
                           maxcol),
                         c('dodgerblue1', 'white', 'yellow', 'orange', 'red')),
        heatmap_legend_param = list(title = 'LogFoldChange'))

>>>>

maxcol <- my_max(stagesTrans_ht.mat)
#Multiply by minus one to use my_max to get the most negative value
mincol <- my_max(stagesTrans_ht.mat*-1)*-1

#Transpose the matrix so that the stages (comparison) are on the x axis like other figures.
ht <- Heatmap(t(stagesTrans_ht.mat),
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        cluster_column_slices = FALSE,
        na_col = 'white',
        #Use factors to keep the ordering that we want.
        row_split = factor(str_extract(colnames(stagesTrans_ht.mat),
                                   pattern = 'pirs|^L|^S|AAPL|ChAPL'),
                              levels = unique(str_extract(colnames(stagesTrans_ht.mat),
                                   pattern = 'pirs|^L|^S|AAPL|ChAPL'))),
        row_order = colnames(stagesTrans_ht.mat),
        row_gap = unit(.5,"cm"),
        row_names_gp = gpar(fontsize = 9),
        border = TRUE,
        #Using this colour scheme because mincol is a lot less negative 
        # than maxcol is positive
        col = colorRamp2(c(mincol,
                           0,
                           maxcol/4,
                           maxcol/2,
                           maxcol),
                         c('dodgerblue1', 'white', 'yellow', 'orange', 'red')),
        heatmap_legend_param = list(title = 'LogFoldChange'))
